A Possibilistic Valid-time Model

### 2011-11-17 trunk/ipmu2012/preliminaries.tex
Last changes for today... I'm getting fuzzy myself...;-)

\subsubsection{Interval Evaluation by Ill-known Constraints}
The problem of the interval evaluation is explained in \cite{Pon11}: For a crisp interval $I = \left[ a, b \right]$, we want to know if all points in this interval reside between the boundaries of the ill-known interval $\left[ X , Y \right]$, where $X,Y$ are ill-known values on the set of real numbers $\mathbb{R}$, and $\lambda$ is the evaluation function.

>>>>

\subsubsection{Interval Evaluation by Ill-known Constraints}
The problem of the interval evaluation is explained in \cite{Pon11}: for a crisp interval $I = \left[ a, b \right]$, the need exists to know if all points in this interval reside between the boundaries of the ill-known interval $\left[ X , Y \right]$, where $X,Y$ are ill-known values on the set of real numbers $\mathbb{R}$, and $\lambda$ is the evaluation function.
